### 2024-02-15 documentation/thesis/thesis_document.tex
.

The next initialisation system is dedicated for multi-sensor
synchronisation \ref{sensor-syncronisation-interface}. The last step in
the setup is to configure communication with the host or connected
\gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
Pico, STM32F4) have a \gls{usb} slave port.

The used usb descriptor is a \gls{usb} \gls{cdc}. This is used to
emulate a virtual RS232 communication port using a \gls{usb} port on a
\gls{pc} and usually no additional driver is needed on modern host
systems.

@@

@@

@@

>>>>

The next initialisation system is dedicated for multi-sensor
synchronisation \ref{sensor-syncronisation-interface}. The last step in
the setup is to configure communication with the host or connected
\gls{pc}. All implemented microcontroller platforms used
(\emph{Raspberry Pi Pico}, \emph{STM32F4}) have a \gls{usb} slave port.

The used usb descriptor is a \gls{usb} \gls{cdc}. This is used to
emulate a virtual \emph{RS232} communication port using a \gls{usb} port
on a \gls{pc} and usually no additional driver is needed on modern host
systems.

@@

The sensor linearity of a magnetic field sensor describes the ability of
the sensor to provide a proportional linear response to changes in the
magnetic field without non-linear distortions. This means that the
output signals of the sensor vary directly proportional to the input
magnetic fields without deviations or distortions and is therefore an
important indicator for measurements of fields at different distances or
objects.

@@

This is achieved here by means of an additional linear axis installed
above the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet was
attached to the end effector of this axis, which can thus be moved at
different distances above the respective sensor \gls{ic}. The ambient
temperature is set to \(\mu_{trev}\)=21.0\(^{\circ}\) in the measurement
runs and thus corresponds to the same conditions as in the
\emph{Background-Noise}\ref{sensor-characterisation-background-noise}
setup.

The figure \ref{Sensor_evaluation_setup_for_linearity_measurements.png}
shows this updated measurement setup with the added components. To
control the linear axis, an additional motion controller of the type
\emph{SKR-Pico} placed outside the temperature chamber is required,
which can be controlled via a network interface. A bash console script
controls the measurement process.

\hypertarget{measurement-setup}{%
\subsection{Measurement Setup}\label{measurement-setup}}

After the sensor baseline has been determined with \emph{N=10000}
samples, the magnet is inserted into the holder. The linear axis is
moved by the user until it is maximally saturated. With the
\emph{TLV493D}, this corresponds to \(\mu_{rev}\)=250.000\(\mu\)T and
below in low resolution mode. \emph{MCC5603NJ} around
\(\mu_{rev}\)=3000\(\mu\)T. This ensures that the linearity is
determined over the entire measuring range.

\hypertarget{measurement-run}{%
\subsection{Measurement Run}\label{measurement-run}}

\hypertarget{linearity-analysis}{%
\subsection{Linearity Analysis}\label{linearity-analysis}}

@@

\ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
